---
title: "Data frames in R"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data frame subsets

There is a ```subset()``` function that allow us to retrieve a specific set of columns or drop a specific set of them. To illustrate it we will first create a simple Data frame.

```{r create_data}
df = data.frame(a =5:9, b = 6:10, c= 7:11)
print(df)
```

Then we can take for example columns "b" and "c" with the following code:

```{r select_bc}
df1 = subset(df, select = c(b,c))
print(df1)
```

Another posible approach to obtain a data frame composed only of the columns "b" and "c" would to drop the column "a":

```{r remove_a}
df2 = subset(df, select = -c(a))
print(df2)
```

## Summary statistics

There are many packages that allow us to obtain the summary statistics of a data frame. An example would be the ```fBasics``` package, which has the ```basicStats(dataFrame)``` function.

Another possibility is to use the do.call functoin in combination with a set of specific functions such as ```mean()```, ```median()```, ```sd()```..., to obtain a specific set of summary statistics:

```{r summary_statistics}
ss = do.call(data.frame, list(
    mean = sapply(df, mean),
    sd = sapply(df, sd),
    median = sapply(df, median),
    min = sapply(df, min),
    max = sapply(df, max)
))
print(ss)
```

