---
title: "Matrices in R"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Initialize a matrix
We can make a 3x4 matrix of zeroes with the following code:

```{r zeroes_matrix}
matrix(0, 3, 4)
```

We can initialize a matrix using a vector of values. Note: if the size of the vector is greater or smaller than the number of cells in the matrix, a warning will be received, but the matrix will be anyway initialized:

```{r init_matrix}
m_init = 1:15
m = matrix(m_init, 3, 4)
print(m)
```

## Change the dimension of a matrix / vector
We can transform a vector into a matrix with the ```dim()``` function. We simply assign a vector that will act as its new dimension

```{r dim_matrix}
dim(m) = c(4,3)
print(m)
```

## Accessing matrix values

Similar to vectors, they can be easily accessed with th "[]" operator

```{r access_matrix}
print(m[1,3])
```

Note: take care when using indexes out of rnge, R doesn't provide a warning an works a bit unconventional (both the follwoing examples should fail).

```{r outofbounds_matrix}
print(m[-1,3])
print(m[0,2])
```

We can get an entire row of the matrix by omitting the column index (but keeping the comma). 

```{r access_row_matrix}
print(m[1,])
```

We can also retrieve multiple rows or columns by providing a vector or sequence with their indices.

```{r access_multiple_column_matrix}
print(m[,2:3])
```