---
title: "Some interesting things about vectors in R"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(out.width='350px', dpi=200)
```

##  Naming vectors

Vectors can have assigned names with the ```names()``` function

```{r names }
numbers = c(1:5)
names(numbers) = c("first", "second", "third", "fourth", "fifth")
numbers
```

## Plotting vectors

The ```barplot()``` function draws a bar chart with a vector's values.

```{r barplot, fig.align='center'}
barplot(numbers)
```

## Arithmetic operations on vectors

When we use arithmetic operations on vectors, they are applied to each element of it.

```{r arithmetic }
numbers + 10
numbers / 2
numbers * 3
```

Other math functions like "sin", "cos" or "sqrt" can be applied to each element of the vector the same way theay are used with numbers:
```{r functions_vector }
sqrt(numbers)
```

## Adding vectors
Vectors can be added or subtracted using the "+", "-" operators when they have the same dimension.

```{r add_vectors }
a = 1:3
b = 5:7
a + b
```

## Comparing vectors

Vectors can also be compared with the "==" operator. This will compare each of their elements and return a vector with its boolean values.

```{r compare_vectors }
a == 2:4
a == 1
a < b
```

