---
title: "scopa-motor analysis"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# SCOPA-MOTOR symptoms analysis

El dataset en cuestión cuenta con 897 instancias y 25 features que representan 21 features reales, de las cuales algunas están duplicadas ya que se refieren a conceptos dobles (dolor izq y derecho por ejemplo).

```{r load_data}
# Loading the data file with 897 complete instances and 137 variables
d897 = read.csv("analysis/clustering/data/897_motor_nms_cluster.csv")

# Filtering the data frame
d897_motor25 = d897[8:32]
```

## Libraries

library(cluster)

## KMeans clustering

### Determine the appropiate number of clusters

Vamos a probar con el gap statistics que parece que es el que mejor va (por pruebas y demas)

#### Gap Statistic

```{r gap_statistic}
d897_motor25_gap = clusGap(x897_motor25, FUN=kmeans, B=500, K.max = 10, nstart = 20, iter.max=30)
print(d897_motor25_gap, "Tibs2001SEmax")
```

### Execute the algorithm for k = 3,4,5

The KMeans algorithm is executed 3 times, storing the resulting models in a new list

```{r kmeans_models}
# first we create a list of NULL values with size = 3
Kmeans_models = vector("list", 3)

# Execute the kmeans algorithm 3 times (k = 2,3,4)
for(i in 1:length(Kmeans_models)){
  Kmeans_models[[i]] = kmeans(x = d897_nms30, centers = i+1, iter.max = 30, nstart = 20)
}
```
